---
title: "SQMB Formative Assessment 2"
author: "EXAM NUMBER"
date: "`r Sys.Date()`"
output: 
  pdf_document: 
    toc: yes
    number_sections: yes
    latex_engine: xelatex
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r attach-pkgs}
# Add the necessary packages here

```


# Instructions

1. **Find a data table** with:
  - One **numeric continuous variable** which is either not-bounded (it can take on any negative and positive number) or it is bounded to positive numbers (note that count data is not continuous).
  - One **categorical (discrete) variable** with two or more levels.

2. Write a very **brief description of the data** and/or study you got the data from to give some context to the analysis you are conducting for this assessment.

  - If possible, state specific research questions or research hypotheses or expectations.

3. **Read and transform the data** as necessary.

4. **Fit a model** with `brm()`.

5. Print the model summary and **describe the main results** (focus on the population-level effects).
  - Report the parameter values of the distributions of the coefficients of the population-level effects.
  - Report the 95% CrIs of the distributions of the coefficients of the population-level effects.

6. **Create plots**.
  - Plot the posterior probability distributions of the population-level effects.
  - Plot the conditional probability distributions.

7. Write a brief statement about your interpretation of the results.
  - Formulate the statement in relation to the research questions/hypotheses and/or expectations from point 2., if any.

# Your code and text



# Render the file

Render this file to PDF by clicking on the "Knit" button. Then submit the PDF file to Learn > Assessment > Formative Assessment 2.
