---
title: "SQMB Formative Assessment 2"
author: "EXAM NUMBER"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = here::here())
```

```{r attach-pkgs}
# Add the necessary packages here

```


# Instructions

1. **Find a data table** with:
  - One **numeric continuous variable** which is either not-bounded (it can take on any negative and positive number) or it is bounded to positive numbers (note that count data is not continuous).
  - One **categorical (discrete) variable** with two or more levels.
2. **Read and transform the data** as necessary.
3. **Fit a model** with `brm()`.
4. Print the model summary and **describe the main results** (focus on the population-level effects).
  - Report the parameter values of the distributions of the coefficients of the population-level effects.
  - Report the 95% CrIs of the distributions of the coefficients of the population-level effects.
5. **Create plots**.
  - Plot the posterior probability distributions of the population-level effects.
  - Plot the conditional probability distributions.

# Your code and text



# Render the file

Before submitting your work, make sure you render this file to HTML by clicking on the "Knit" button. The submission must include the HTML file too.
